Understanding the problem

### 2024-04-17 presentations/understanding the problem.qmd
commutativity

@@

:::: {.columns}

::: {.column width="30%"}
Same data gave different indicator values
:::

@@

::: aside
Indicators with grey background
:::
:::

::::

@@

---

@@

---

Adding area weighting to the first example
```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example3b.R")
example3b
```

---

and to the second example
```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example5.R")
example5
```

---

>>>>

```{r setup}
library(knitr)
```

@@

::: columns
::: {.column width="30%"}
Same data gave different indicator values
:::

@@

::: aside
Indicators with grey background
:::
:::
:::

@@

------------------------------------------------------------------------

@@

------------------------------------------------------------------------

Adding area weighting to the first example

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example3b.R")
example3b
```

------------------------------------------------------------------------

and to the second example

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example5.R")
example5
```

## Commutativty

These are examples of cummutative aggregation workflows

![](img/commutativity.PNG)

------------------------------------------------------------------------
